---
title: Conor Higgins' Resume"
author: Conor Higgins
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 

```


Aside
================================================================================




Contact {#contact}
--------------------------------------------------------------------------------



- <i class="fa fa-envelope"></i> conormjhiggins@gmail.com
- <i class="fa fa-twitter"></i> [conormjhiggins](https://twitter.com/conormjhiggins)
- <i class="fa fa-github"></i> [github.com/conormjhiggins](https://github.com/conormjhiggins)
- <i class="fa fa-phone"></i> (+44) 7728 434048



Language & Visualisation Skills {#skills}
--------------------------------------------------------------------------------

Highly Skilled

- R 
- LaTeX
- Microsoft Office (Including Excel, VBA, PowerPoint etc.)
- SAS
- Shiny
- Markdown

Experience With

- Python 3 (Currently learning)
- HTML
- Tableau
- Power BI (Currently learning)
- Matlab
- STATA
- SQL

Relevant Package Knowledge {#packages}
--------------------------------------------------------------------------------
- ggplot2
- tm
- dplyr
- caret
- shiny
- esquisse
- lubridate
- janitor 
- stringr
- glue
- RSQLite
- plotly
- etc


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/conormjhiggins/cv](https://github.com/conormjhiggins/cv).

Last updated on `r Sys.Date()`.




Main
================================================================================

Conor Higgins {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- "I am a recent graduate of Lancaster University, looking to further my short career within the Data Science/Statistics field. I believe that I am an outstanding communicator and leader with high levels of determination and motivation. Excellent ability to bring enthusiasm, focus, and a positive demeanor to the workplace. Flexible, dependable, and eager to work both independently as well as in a team towards aims and goal. I am a confident public speaker and consider myself people person as I have led and participated within teams throughout my entire life. I believe that I am a great problem solver and would be a valuable asset to any team."

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```



Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```


Interests & Other {data-icon=user}
--------------------------------------------------------------------------------

Alongside my experience I am also a keen learner of multiple fields, and try to partake in multiple hobbies. To help my statistical experience I take part in [TidyTuesday](https://github.com/rfordatascience/tidytuesday) weekly. I am also an avid snooker and football player at an amateur level, of which I have captained both of my teams adding to my leadership experience throughout my life. The love of football also fuels my drive to perform analytics on the sport, whilst also pursuing coaching badges.